\runsubsection{Quosphere Infosolutions Pvt. Ltd.}
\descript{| Junior Data Scientist }
\location{Jul 2020 – Dec 2021 | Navi Mumbai}
\vspace{\topsep}

\project{Spiritzone Product Recommender System}

\keywordlight{Python} \textbullet{} \keywordlight{Flask} \textbullet{} \keywordlight{Collaborative Filtering} \textbullet{} \keywordlight{Content based recommender system} 

\begin{tightemize}
\item A hybrid recommender system trained using user's product browsing patterns and feedback path drawn from customer engagement platforms where the models are incrementally trained using the customer interaction data.
\item Highly scalable and easily maintainable stateless microservices developed using Python and Flask. Capable of handling 30+ requests per second asynchronously.
\item End to end unit \& integration tested using python's built-in unit test library
\end{tightemize}

\project{Market Basket Analysis}

\keywordlight{Python} \textbullet{} \keywordlight{FastAPI} \textbullet{} \keywordlight{Apriori Algorithm} \textbullet{} \keywordlight{Docker compose} \textbullet{} \keywordlight{FP-Growth Algorithm}

\begin{tightemize}
\item Developed using the \keyword{Apriori} and \keyword{FP-Growth} algorithm for efficient, scalable and maintainable stateless microservice.
\item Used FastAPI and Docker to make the deployment process easier alongside a complete build pipeline, capable of training the the models on a daily basis.
\item Unit tests with 90\%+ code coverage \& successfully handled load testing with 30+ concurrent requests per second (conducted using Locust).
\end{tightemize}

\project{Clickstream Data Analytics Pipeline}

\keywordlight{Azure Data Explorer} \textbullet{} \keywordlight{Python} \textbullet{} \keywordlight{Grafana}

\begin{tightemize}
\item A data pipeline using azure's python SDK and Azure Data Explorer to move huge volume of data incrementally.
\item Scheduled reports that gets sent out everytime data ingestion process has been finished.
\item Dynamically controlling frequency of ingestion without losing any data.
\end{tightemize}